\chapter*{\centering Dedication}
This work is wholeheartedly dedicated to my beloved parents Mokhtar and Fouzia, and my brothers Ahmed and Seddik and my sister Meriem for the support on all levels, who have been my source of inspiration; whose affection, love, encouragement and prays of day and night make me able to get such success and honor. I also extend my gratitude and congratulations to my partner Malik for the good work that he did despite facing hard personal challenges as well as my friends, relatives, mentor, teachers, classmates who have been all along.
\\
\\
\\
\\
\begin{Large}
  \textbf{Mehieddine Boudissa}
\end{Large}

\chapter*{\centering Dedication}
I dedicate my dissertation work to my family and many friends. A special
feeling of gratitude to my loving parents, Mohammed and Ouiza  whose
words of encouragement and push for tenacity ring in my ears. My sisters Dihia,
and Lydia have never left my side and are very special.
 I also dedicate this dissertation to my many friends and classmates who have
supported me throughout the process. I will always appreciate all they have done,
especially Djamel Eddine Zidane and AbdelMalek Bouaoune who reminded me, all along, with the importance of our religion and kept motivating
and pushing me to read Quran and never neglect it whatever how desperate the situation may seem.
I dedicate this work and give special thanks to my partner Mehieddine for being there for me throughout my struggle and kept faith with me.
\\
\\
\\
\\
\begin{Large}
  \textbf{Malik KISSOUM}
\end{Large}
